Viscous Transport in Eroding Porous Media

### 2019-08-10 docs/transport/erosion_transport.tex
small changes throughout

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense101}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the
forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
has almost completely eroded.}
\end{center}
\end{figure}

@@

In this example, we also observe that erosion creates a network of
channels from the inlet to outlet where the velocity and vorticity, and
therefore erosion rate, are much larger than the other regions.  These
channels can be further visualized by considering the streamlines.  In
Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
time step from Figure~\ref{fig:Eroding20vort}, and we simulate 200
tracers.  The tracers are initially placed at $x=-1$ and are equispaced
in $y$.  The trajectories are shown at 5 different times, and the final
plot is a zoom in of the lower right quadrant of the fifth time step.
There are three clear regions where the tracers pass through the
geometry fastest.  Two of these regions are located between the bodies
and the solid walls at $y=\pm 1$, and the third cuts through the porous
region with the upper part of the channel formed by bodies 1, 4, 6, and
8.  Since the flow is fastest in these regions, the shearing is largest,
and this causes these openings to grow fastest which can be observed in
Figure~\ref{fig:Eroding20vort}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
the second geometry from Figure~\ref{fig:Eroding20vort}. The tracers are
initialized at $x=-1$ and are evenly spaced in the $y$-direction. The
first five snapshots are evenly spaced in time.  The bottom right frame
is a zoom window of the fifth snapshot.  Since we use a Barycentric
quadrature rule and the fourth-order Runge-Kutta method, the tracers can
be very close to but not penetrate the bodies.}
\end{center}
\end{figure}

@@

In Figure~\ref{fig:Eroding20tort_all}, we plot the tortuosity as a
function of the porosity from the initial porosity of $0.38$ until all
the bodies have eroded.  The tortuosity is computed with both the
length of the Lagrangian trackers~\eqref{eqn:tortuosity1} and using the
spatial average of the velocity on an Eulerian
grid~\eqref{eqn:tortuosity2}.  The red square mark corresponds to the
porosity in Figure~\ref{fig:Eroding20tort}(c).  The two methods of
calculating the tortuosity give similar results with any discrepancy
being accounted for by slow regions of recirculation.  Computing the
velocity on an Eulerian grid is computationally easier than simulating
many trajectories, so we use the Eulerian approach for all future
examples.  As the bodies erode, this creates wide channels where
trajectories undergo only minor vertical deflections, and this explains
why the tortuosity eventually decreases with porosity.  However, at the
early stages of the erosion, the tortuosity increases with porosity,
which can be explain as follows.   In the absence of erosion
(left plot in Figure~\ref{fig:Eroding20vort}), many of the trajectories,
such as those initialized between bodies 15 \& 18, only perform minor
deflections to pass through the narrow regions, albeit, very slowly.
However, as erosion starts to open the channels, the trajectories
deflect into the fast regions, and this increases the amount of vertical
deflection, and therefore the tortuosity.
\todo[inline]{BQ: Need to work on this paragraph}

>>>>

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense101}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.225\textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The four snapshots are evenly spaced in time. We use $N_\iin
= 256$ discretization points on the bodies and $\Dt=10^{-4}$.  In the
forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
has almost completely eroded.}
\end{center}
\end{figure}

@@

In this example, we also observe that erosion creates a network of
channels from the inlet to outlet where the velocity and vorticity, and
therefore erosion rate, are much larger than in other regions.  These
channels can be further visualized by considering the streamlines.  In
Figure~\ref{fig:Eroding20tracer}, we freeze the geometry at the second
time step from Figure~\ref{fig:Eroding20vort}, and we plot 200
trajectories that are initialized at $x=-1$ and equispaced in $y$.  The
trajectories are shown at 5 different times, and the final plot is a
zoom in of the lower right quadrant of the fifth time step.  There are
three clear regions where the tracers pass through the geometry fastest.
Two of these regions are located between the bodies and the solid walls
at $y=\pm 1$, and the third cuts through the porous region with the
upper part of the channel formed by bodies 1, 4, 6, and 8.  Since the
flow is fastest in these regions, the shearing is largest, and this
causes these openings to grow fastest which can be observed in
Figure~\ref{fig:Eroding20vort}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20tracer}200 trajectories in the second
geometry from Figure~\ref{fig:Eroding20vort}. The trajectories are
initialized at $x=-1$ and are equally spaced in the $y$-direction. The
first five snapshots are evenly spaced in time.  The bottom right frame
is a zoom window of the fifth snapshot.  Since we use a Barycentric
quadrature rule and the fourth-order Runge-Kutta method, the tracers can
be very close to but not penetrate the bodies.}
\end{center}
\end{figure}

@@

In Figure~\ref{fig:Eroding20tort_all}, we plot the tortuosity as a
function of the porosity from the initial porosity of $0.38$ until all
the bodies have eroded.  The tortuosity is computed with both the length
of the trajectories~\eqref{eqn:tortuosity1} (red marks) and using the
spatial average of the velocity on an Eulerian
grid~\eqref{eqn:tortuosity2}.  The red square corresponds to the
porosity in Figure~\ref{fig:Eroding20tort}(c).  The methods give similar
results with any discrepancy being accounted for by slow regions of
recirculation.  As the bodies erode, this creates wide channels where
trajectories undergo only minor vertical deflections, and this explains
why the tortuosity eventually decreases with porosity.  The increase in
tortuosity for small porosities occurs because in the absence of erosion
(left plot in Figure~\ref{fig:Eroding20vort}), many of the trajectories,
such as those initialized between bodies 15 \& 18, only perform minor
deflections to pass through the narrow regions, albeit, very slowly.
However, as erosion starts to open the channels, the trajectories
deflect into the fast regions, such as the region above body 11, and
this increases the amount of vertical deflection, and therefore the
tortuosity.
